---
title: "P8105_hw1_jam2530"
date: September 23 2023
author: Jenna Mohammed
output: github_document
---

```{r warning=FALSE}
library(moderndive)
library(tidyverse)
```


```{r warning=FALSE}
data("early_january_weather")

```


# Problem 1

```{r}
# Calculating information about table

early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)
```


```{r}
# Calculating mean of temperature

mean(pull(early_january_weather, temp))
```


Table Description: The table shows that there are 358 rows and 15 columns. Important variables in this dataset are hour, temperature, dewpoint, humidity,wind direction, wind speed, and pressure. The information is repeatedly collected every hour from hour 1 to hour 23. The mean of the temperature is 39.58212


```{r}
# Creating scatterplot for time_hour vs temperature

plot_df = tibble(
    x = "time_hour",
    y = "temp"

)

ggplot(early_january_weather, aes(x = time_hour , y = temp , color = humid )) + geom_point()
      
ggsave("P8105_hw1_jam2530.pdf")                                                                        
```

Plot Description: The plot shown expressed the relationship between time_hour and temperature, with time_hour represented on the x axis and temperature represented on the y axis. The graph shows a moderately strong positive relationship. There are no apparent outliers, but around January 12th/13th the data strayes from the pattern.


# Problem 2

This code chunk shows the creation of a data frame. 

```{r}
Homework_df = tibble(
        samp = rnorm(10),
        vec_logical = samp > 0,
        vec_char = c("1", "2", "3", "4" , "5" , "6" , "7", "8" , "9" , "10"),
        vec_factor = c("LOW", "MED", "HIGH", "LOW", "LOW", "MED", "HIGH", "LOW", "MED", "HIGH"),
    )

```

This code chunk will take the mean of each variable in the data frame.
```{r}
# taking the mean of each variable

mean(Homework_df[["samp"]])
mean(Homework_df[["vec_logical"]])
mean(Homework_df[["vec_char"]])
mean(Homework_df[["vec_factor"]])

```

This code chunk will convert variables from one type to another.

```{r}
as.numeric(Homework_df[["vec_logical"]])
as.numeric(Homework_df[["vec_char"]])
as.numeric(Homework_df[["vec_factor"]])
```


Mean/as.numeric description: When taking the as.numeric of "vec_factor", an error occurs. There is an error when trying to compute the mean for it as well since it is categorized as "low", "med", and "high". This cannot be converted into numerical values and therefore cannot give you a mean.
