---
title: "P8105_hw1_jam2530"
date: September 19 2023
name: "Jenna Mohammed"
output: html_document
---

```{r}
library(moderndive)
library(tidyverse)
```


```{r}
data("early_january_weather")
```


# Problem 1

```{r}
# Calculating information about table

early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)
```


```{r}
# Calculating mean of temperature

mean(pull(early_january_weather, temp))
```


The table shows that there are 358 rows and 15 columns.The information is repeatedly collected every hour from hour 1 to hour 23. The mean of the temperature is 39.58212


```{r}
# Creating scatterplot for time_hour vs temperature

plot_df = tibble(
    x = "time_hour",
    y = "temp"

)

ggplot(early_january_weather, aes(x = time_hour , y = temp , color = humid )) + geom_point()
                                                                              
```

The plot shown expressed the relationship between time_hour and temperature, with time_hour represented on the x axis and temperature represented on the y axis. The graph shows a moderately strong positive relationship. There are no apparent outliers, but around January 12th/13th the data strayes from the pattern.


# Problem 2

```{r}
samp = rnorm(10)
```

